maxent model avec xvalidation (year-based test training)

### 2019-05-02 src/maxent_avec_xvalidation.Rmd
cbi added

    mod <- maxent(x = train, p = trainpa, path = paste0("../output/maxent/models/", timeslice), args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "addsamplestobackground=TRUE", paste0("betamultiplier=", betaval)))

@@

>>>>

    mod <- maxent(x = train, p = trainpa, path = paste0("../output/maxent/models/", timeslice), args=c("writebackgroundpredictions=TRUE",  "maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "addsamplestobackground=TRUE", paste0("betamultiplier=", betaval)))

@@

#cbi
use enmSdm package? see exercise 10...
positive values are good!

should move this up to evaluation....

```{r}

for (a in 1:length(modelmonth)){
  timeslice <- modelmonth[a]
  yr <- str_sub(timeslice, -4) #the year being used for testing
  predPres <- read.csv(paste0("../output/maxent/models/", a, "/species_samplePredictions.csv"), header = TRUE)
  predBg <- read.csv(paste0("../output/maxent/models/", a, "/species_backgroundPredictions.csv"), header = TRUE)
  predPres <- predPres$Cloglog.prediction
  predBg <- predBg$Cloglog
  cbi <- contBoyce(pres = predPres, bg = predBg)
}

predPres <- read.csv("../output/maxent/models/jan2003/species_samplePredictions.csv", header = TRUE)
predBg <- read.csv("../output/maxent/models/jan2003/species_backgroundPredictions.csv", header = TRUE)
predPres <- predPres$Cloglog.prediction
predBg <- predBg$Cloglog
cbi <- contBoyce(pres = predPres, bg = predBg)
cbi
```
